### 2015-04-07 rscripts/data_review.Rmd
implementing bus method one

```{r, echo=FALSE}
src.dt <- fread("~/Dropbox/montreal/merged.o", header = F, sep=" ")
setnames(src.dt, c("user_id", "location_id", "login", "logout"))
setkey(src.dt, login, logout, user_id, location_id)
src.dt
```

@@

```{r, echo=FALSE}
censor.dt <- src.dt[(logout - login) <= max_hours*60*60, ]
invalid.users <- censor.dt[,.N, by=user_id ][N < min_logins, user_id]
while(length(invalid.users) > 0) {
  censor.dt <- censor.dt[!user_id %in% invalid.users]
  invalid.locs <- censor.dt[,.N, by=location_id ][N < min_logins, location_id]
  censor.dt <- censor.dt[!location_id %in% invalid.locs]
  invalid.users <- censor.dt[,.N, by=user_id ][N < min_logins, user_id]
}
```

@@

# src.dt <- fread("~/Dropbox/montreal/merged.o", header = F, sep=" ")
# setnames(src.dt, c("user_id", "location_id", "login", "logout"))
# setkey(src.dt, login, logout, user_id, location_id)
# max_real_duration <- 60*60*24 # at most, continuous login of a day

>>>>

```{r, echo=FALSE}
src.dt <- fread("~/Dropbox/montreal/merged.o", header = F, sep=" ", colClasses = c("integer","integer","integer","integer"))
setnames(src.dt, c("user_id", "location_id", "login", "logout"))
setkey(src.dt, login, logout, user_id, location_id)
src.dt
```

@@

```{r, echo=FALSE}
censor.dt <- src.dt[(logout - login) <= max_hours*60*60, ]
invalid.users <- censor.dt[,.N, by=user_id ][N < min_logins, user_id]
while(length(invalid.users) > 0) {
  censor.dt <- censor.dt[!user_id %in% invalid.users]
  invalid.locs <- censor.dt[,.N, by=location_id ][N < min_logins, location_id]
  censor.dt <- censor.dt[!location_id %in% invalid.locs]
  invalid.users <- censor.dt[,.N, by=user_id ][N < min_logins, user_id]
}
censor.dt
```

Relabel source data:

1. re-assign user ids from 1, ordered by first appearance
2. re-assign location ids from 1, ordered by first appearance
3. TODO split entries that cross days (~ 3% of data; of crossing entries, most look like late PM->early AM sessions, aka bar / club visits)
4. convert login / logout times to `log(in|out)_day` and `log(in|out)_time`

```{r, echo=FALSE}
censor.dt[,
  user_id := .GRP, by=user_id
][,
  location_id := .GRP, by=location_id
][,
  login_day := login %/% (24*60*60)
][,
  logout_day := logout %/% (24*60*60)
][,
  login_time := login - login_day*24*60*60
][,
  logout_time := logout - logout_day*24*60*60
]
setkey(censor.dt, login, logout, user_id, location_id)
save(censor.dt, file = "~/Dropbox/montreal/censored.Rdata")
# censor.dt[,list(
#   login_day = login %/% (24*60*60),
#   logout_day = logout %/% (24*60*60),
#   login_time = login %% (24*60*60)/(60*60),
#   logout_time = logout %% (24*60*60)/(60*60)
# ) ]
```

@@
